State of the Art Review on Privacy-Preserving Signatures, Credentials, and Authentication

### 2021-11-09 prism-backend/research/soa_review/ac.tex
Summary of CKL+15. Nice.

  sign vectors of messages, including commitments.

@@

\begin{enumerate}
\item[\cite{cl01}:] Security in \cite{cl01} is proven in an ad-hoc way,
  using the ideal-world/real-world paradigm. The authors describe a
  simulator for the operations supported by the system (Setup, FormNym,
  GrantCred, VerifyCred and VerifyCredOnNym), and prove that the output of this
  simulator is indistinguishable from that of the real protocol, under the
  strong RSA and Diffie-Hellman assumptions.  
\item[\cite{cl02}:] No security model is given for the anonymous credential
  application of the signature scheme (reasonably, as it is not the main focus
  of the paper). The signature scheme is proven secure (no specific mention
  to a security model, although I suppose it would be quite straight forward)
  based on the Strong RSA and Diffie-Hellman assumptions.
\item[\cite{cl04}:] Same as in \cite{cl02} (no actual security model for the
  AC system). The custom proofs are based on the DDH and LRSW assumptions.
\item[\cite{cks10}:] Signer privacy and user privacy properties are required
  for the underlying signature scheme (thus, inherited by the credential system,
  although I have not found explicit model). Signer privacy captures that the
  adversary (including corrupt users) doesn't learn any information about the
  signer from signatures and updates of signatures. User privacy captures that
  the adversary (including a corrupt issuer) does not learn any information
  about the blindly signed messages. \doubt{Not sure I get the utility of
    signer privacy. The original property seems to come from \cite{bckl08}.}
\item[\cite{cmz14}:] The security properties proven in this work are:
  \begin{itemize}
  \item \emph{Unforgeability}: The adversary cannot produce a valid proof for a
    statement, if none of the attribute sets for which it has received a
    credential meets that statement.
  \item \emph{Anonymity}: The proofs produced in a presentation do not leak
    more information than the statement being proved.
  \item \emph{Blind issuance}: The issuance protocol is a secure two-party
    protocol for generating credentials on th euser's attributes.
  \item \emph{Key-parameter consistency}: no issuer can use different parameters
    to produce credentials of different users such that their anonymity can
    be compromised afterwards. \doubt{This somehow remembers non-frameability in
      group signatures.}
  \end{itemize}
\item[\cite{cdhk15}:] The model (and associated proofs) presented in this paper
  is very comprehensive, and detailed. Specifically, for the main building block
  (Unlinkable Redactable Signatures), the authors give both game-based
  definitions as well as an ideal functionality. This ideal functionality models
  security in a single-issuer setting. However, as it is done in the UC
  framework, it can be composed with itself, so that a scenario with multiple
  issuers, in which users can combine credentials obtained by different users
  into a single showing process (``presentation'') is directly achievable by
  composing multiple instances of the ideal functionality (one per ``proof
  part'').
\item[\cite{dmm+18}:] The authors give a game-based security model, covering
  properties of unforgeability, anonymity, and policy-hiding. The latter
  means that, for delegated verification, the verifier is oblivious to the
  policy being verified.
\item[\cite{sms+19}:] No security model is given nor adopted.
\end{enumerate}

@@

\begin{itemize}
\item \cite{bcc+09}: Delegation.
\item \cite{fhs19}: Structure-preserving signatures for AC.
\item \cite{aks12}: ACs with revocation.
\item \cite{ckl+15}: Formal treatment of privacy-preserving credentials.
\end{itemize}

>>>>

  sign vectors of messages, including commitments. Here, as in the seminal
  works by Camenisch and Lysyanskaya \cite{cl01,cl02,cl04}, pseudonyms are
  used as explicit building blocks. \todo{Not sure yet of how they are
    made explicit in the generic construction. Clarify.}
  A ``syntactic'' variation: they introduce
  the concept of tokens both for credential issuance and presentation. To
  request issuance of a credential, users have to produce an issuance token
  from the set of attributes they want to reveal to the issuer, and the set
  of attributes they want to hide (potentially coming from another credential
  already owned by the user). An equivalent description applies for presentation
  of a credential to a verifier. In both cases, the issuer/verifier has to
  check the received token prior to issuing a credential or granting access.
  They also add revocation functionality. For this, a revocation authority
  (not necessarily the issuer) keeps a revocation information list, which is
  basically a list containing no longer valid attributes. In order to prove
  that their credentials are valid w.r.t. some attribute, users have to generate
  a (non) revocation token, which proves that the attribute has not been
  included in the revocation information list.

@@

\item[\cite{cl01}:] Security in \cite{cl01} is proven in an ad-hoc way,
  using the ideal-world/real-world paradigm. The authors describe a
  simulator for the operations supported by the system (Setup, FormNym,
  GrantCred, VerifyCred and VerifyCredOnNym), and prove that the output of this
  simulator is indistinguishable from that of the real protocol, under the
  strong RSA and Diffie-Hellman assumptions.  
\item[\cite{cl02}:] No security model is given for the anonymous credential
  application of the signature scheme (reasonably, as it is not the main focus
  of the paper). The signature scheme is proven secure (no specific mention
  to a security model, although I suppose it would be quite straight forward)
  based on the Strong RSA and Diffie-Hellman assumptions.
\item[\cite{cl04}:] Same as in \cite{cl02} (no actual security model for the
  AC system). The custom proofs are based on the DDH and LRSW assumptions.
\item[\cite{cks10}:] Signer privacy and user privacy properties are required
  for the underlying signature scheme (thus, inherited by the credential system,
  although I have not found explicit model). Signer privacy captures that the
  adversary (including corrupt users) doesn't learn any information about the
  signer from signatures and updates of signatures. User privacy captures that
  the adversary (including a corrupt issuer) does not learn any information
  about the blindly signed messages. \doubt{Not sure I get the utility of
    signer privacy. The original property seems to come from \cite{bckl08}.}
\item[\cite{cmz14}:] The security properties proven in this work are:
  \item \emph{Unforgeability}: The adversary cannot produce a valid proof for a
    statement, if none of the attribute sets for which it has received a
    credential meets that statement.
  \item \emph{Anonymity}: The proofs produced in a presentation do not leak
    more information than the statement being proved.
  \item \emph{Blind issuance}: The issuance protocol is a secure two-party
    protocol for generating credentials on the user's attributes.
  \item \emph{Key-parameter consistency}: no issuer can use different parameters
    to produce credentials of different users such that their anonymity can
    be compromised afterwards. \doubt{This somehow remembers non-frameability in
      group signatures.}
\item[\cite{cdhk15}:] The model (and associated proofs) presented in this paper
  is very comprehensive, and detailed. Specifically, for the main building block
  (Unlinkable Redactable Signatures), the authors give both game-based
  definitions as well as an ideal functionality. This ideal functionality models
  security in a single-issuer setting. However, as it is done in the UC
  framework, it can be composed with itself, so that a scenario with multiple
  issuers, in which users can combine credentials obtained by different users
  into a single showing process (``presentation'') is directly achievable by
  composing multiple instances of the ideal functionality (one per ``proof
  part'').
\item[\cite{ckl+15}:] The main security and privacy properties required are
  pseudonym collision-resistance (two different user secret keys cannot produce
  the same nym for the same scope), unforgeability (the adversary cannot forge
  issuance tokens or presentation tokens), and privacy (no two presentations by
  the same user can be linked) or weak privacy (presentations by the same user
  can be linked, but not traced to an issuance session). Privacy is modelled
  in the simulation paradigm, the difference in the modelling between privacy
  and weak privacy being a filter that removes some information \note{(I find
    this kind of weird; probably I'm wrong. Would be nice to study further)}.
  The unforgeability and privacy properties are essentially inherited from the
  main building block, privacy-enhancing attribute-based signatures. Although
  there, the authors begin by defining a blind issuance experiment (ensuring
  that the issuer does not learn anything more than what it should during
  isusance), and then define two variants for user privacy: presentation privacy
  and untraceability, which basically match the strong and weak notions for
  PABCs (in untraceability, two presentations by the same user can be linked,
  but not trace to a specific credential issuance). [Strong] user privacy has
  to satisfy both blind issuance and presentation privacy; weak user privacy
  has to satisfy both blind issuance and untraceability. I find this model
  somehow interesting, as it is one of the few (maybe along with \cite{cmz14})
  that includes some notion related to tracing back to issuance of credentials,
  as in group signatures). In both cases (PABC and PABS), [strong] privacy
  implies weak privacy.
  Essentially, the security properties required by the PABC scheme, are
  ensured by the building blocks. Namely: the pseudonym system (requiring
  key extractability, collision resistance and pseudonym unlinkability); the
  revocation scheme (requiring soundness and revocation privacy); the
  PABs (requiring unforgeability, and [weak] privacy); and the commitment
  scheme (requiring blinding and hiding, and opening extractability).
\item[\cite{dmm+18}:] The authors give a game-based security model, covering
  properties of unforgeability, anonymity, and policy-hiding. The latter
  means that, for delegated verification, the verifier is oblivious to the
  policy being verified.
\item[\cite{sms+19}:] No security model is given nor adopted.

@@

\begin{itemize}
\item \cite{bcc+09}: Delegation.
\item \cite{fhs19}: Structure-preserving signatures for AC.
\item \cite{aks12}: ACs with revocation.
\end{itemize}
